Supplement to Automatic Matching of Bullet Lands

### 2016-01-06 imaging-supplement.Rnw
reference to file corrected

#bstats <- read.csv("data-25-25/bullet-stats.csv")
#flagged <- c("Br6 Bullet 2-1", "Br9 Bullet 2-4", "Ukn Bullet B-2", "Ukn Bullet Q-4")
includesVar <- setdiff(names(ballstats), c("b1", "b2", "data", "resID", "id.x", "id.y", "id", "pred", "forest", "bullet", "span", "crosscutdist", "flagged", "km", "forestsmall",
                                        "left_cms", "right_cms", "left_noncms", "right_noncms"))

@@

ballstats <- read.csv("data-new-all-25-25/bullet-stats-single.csv")
# names(ballstats)[10] <- "num.nonmatches"
# names(ballstats)[11] <- "CNMS"
# names(ballstats)[16] <- "S"
# names(ballstats)[17] <- "CMS"
#ballstats$forestsmall <- predict(rtrees, newdata=ballstats, type="prob")[,2]
###########

>>>>

#bstats <- read.csv("data-25-25/bullet-stats.csv")
#flagged <- c("Br6 Bullet 2-1", "Br9 Bullet 2-4", "Ukn Bullet B-2", "Ukn Bullet Q-4")
ballstats <- read.csv("data-new-all-25-25/bullet-stats-single.csv")

includesVar <- setdiff(names(ballstats), c("b1", "b2", "data", "resID", "id.x", "id.y", "id", "pred", "forest", "bullet", "span", "crosscutdist", "flagged", "km", "forestsmall",
                                        "left_cms", "right_cms", "left_noncms", "right_noncms"))

@@

# names(ballstats)[10] <- "num.nonmatches"
# names(ballstats)[11] <- "CNMS"
# names(ballstats)[16] <- "S"
# names(ballstats)[17] <- "CMS"
#ballstats$forestsmall <- predict(rtrees, newdata=ballstats, type="prob")[,2]
###########
